Pool Model

### 2023-12-20 pool_model.tex
change description and shown example

        \subcaption{Inhomogenous initial cell distribution, $D_R=D_I=30.0$\unit{\micro\metre\squared\per\minute}}

@@

        \includegraphics[width=\textwidth]{Figures/abm-inhomogenous-low-diffusion/abm_ode_comparison.png}%
        \subcaption{Inhomogenous initial cell distribution, $D_R=D_I=5.0$\unit{\micro\metre\squared\per\minute}}

@@

        In subfigure (d), due to the heterogenous cell distribution (see also~\ref{fig:supplement-spatial-initial-config-cells}) and slow diffusion, overall inhibition of species $B$ does not play as large of a role.

@@

        \includegraphics[width=\textwidth]{Figures/abm-inhomogenous-low-diffusion/snapshot_00012000.png}%
        \subcaption{Inhomogenous initial cell distribution, $D_R=D_I=5.0$\unit{\micro\metre\squared\per\minute}}

>>>>

        \subcaption{Heterogeneous initial cell distribution, $D_R=D_I=30.0$\unit{\micro\metre\squared\per\minute}}

@@

        \includegraphics[width=\textwidth]{Figures/abm-random/abm_ode_comparison.png}%
        \subcaption{Randomized initial cell distribution, $D_R=D_I=5.0$\unit{\micro\metre\squared\per\minute}}

@@

        In subfigure (c), due to the heterogenous cell distribution (see also~\ref{fig:supplement-spatial-initial-config-cells}), overall inhibition of species $B$ is significantly reduced.
        Subfigure (d) shows how a randomized homogenous initial distribution can lead to even more notable effects of inhibition.

@@

        \includegraphics[width=\textwidth]{Figures/abm-random/snapshot_00012000.png}%
        \subcaption{Random initial cell distribution, $D_R=D_I=5.0$\unit{\micro\metre\squared\per\minute}}
